---
title: "Demo flexdashboard + htmlwidgets + crosstalk"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(DT)
library(crosstalk)

shared_mtcars <- SharedData$new(mtcars)
```


Inputs {.sidebar}
--------------------------------------------------------------------------------


```{r}
crosstalk::filter_checkbox("cyl", "Cylinders", shared_mtcars, ~cyl, inline = TRUE)
crosstalk::filter_slider("hp", "Horsepower", shared_mtcars, ~hp, width = "100%")
crosstalk::filter_select("auto", "Automatic", shared_mtcars, ~ifelse(am == 0, "Yes", "No"))
```




Row {.tabset}
--------------------------------------------------------------------------------

### Table `{DT}`

```{r}
datatable(shared_mtcars)
```

### Data

\

`mtcars`: The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

* `mpg` - Miles/(US) gallon
* `cyl` - Number of cylinders
* `disp` - Displacement (cu.in.)
* `hp` - Gross horsepower
* `drat` - Rear axle ratio
* `wt` - Weight (1000 lbs)
* `qsec` - 1/4 mile time
* `vs` - Engine (0 = V-shaped, 1 = straight)
* `am` - Transmission (0 = automatic, 1 = manual)
* `gear` - Number of forward gears
* `carb` - Number of carburetors



Row
--------------------------------------------------------------------------------


### Chart A `{plotly}`

```{r}
#d3scatter(shared_mtcars, ~wt, ~mpg, ~factor(cyl), width="100%", height=250)

plot_ly(shared_mtcars, 
        x = ~wt, 
        y = ~mpg, 
        color = ~factor(cyl),
        type = 'scatter',
        mode = 'markers',
        width = NULL,
        height = 250) %>%
  layout(
    xaxis = list(title = "wt"),
    yaxis = list(title = "mpg"),
    legend = list(title = list(text = "cyl"))
  )
```

### Chart B `{plotly}`

```{r}
#d3scatter(shared_mtcars, ~hp, ~qsec, ~factor(cyl), width="100%", height=250)

plot_ly(shared_mtcars, 
        x = ~hp, 
        y = ~qsec, 
        color = ~factor(cyl),
        type = 'scatter',
        mode = 'markers',
        width = NULL,
        height = 250) %>%
  layout(
    xaxis = list(title = "wt"),
    yaxis = list(title = "mpg"),
    legend = list(title = list(text = "cyl"))
  )
```



